An Open-Source Implementation of the CMPS Algorithm for Assessing  Similarity of Bullet Signatures

### 2021-05-27 CMPSpaper_writing/CMPSpaper_writing.Rmd

@@

>>>>

\hh{XXX include some signatures here.}

```{r echo=FALSE, fig.cap="Signatures of all lands of bullet 1 in the top row, and of bullet 2 in the bottom row. Signatures in the second row are ordered to be in phase with the signatures above, i.e. ..."}
signatures <- bullets %>% unnest(sigs)
signatures <- signatures %>% mutate(
  bulletland = factor(bulletland, levels=c(paste(rep(c(1,2), each=6), c(1:6,2:6,1), sep="-")))
)
signatures %>% ggplot(aes(x = x/1000, y = sig)) + geom_line() + facet_wrap(~bulletland, ncol=6) +
  theme_bw() +
  xlab("Length in mm") +
  ylab("Relative height in micron")
```

@@

one of a pair of signatures that are known to be a match -- a KM (known match) comparison
